\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}
 
% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Alexander Mikhailov}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{website.com}
% vs how you want it to show up. If it's the same you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourWebsiteLink}{https://website.com}
\newcommand{\yourEmail}{alexander.mikhailoff@gmail.com}
\newcommand{\yourPhone}{+7 (926) 419-78-25}
\newcommand{\githubUserName}{avtomatik}
\newcommand{\linkedInUserName}{alexander-mikhailov-59a84243}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{PhD Mathematical and Instrumental Methods of Economics}{State University of Management, Information Systems Institute}{Moscow, Russia}{On Hold}

\educationHeading{Specialist Magna Cum Laude Management}{State University of Management, National and World Economy Institute}{Moscow, Russia}{Jun 2011}

% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Willis Towers Watson}{Broker}{Moscow, Russia}{Nov 2018 - Nov 2022}
\begin{bullets}
    \item Supported Team with Servicing the Portfolio of over 50 Accounts of Largest Oil \&
    Gas Clients.
    \item Designed, Developed and Supported Paperwork Service Using \textbf{Python3} Libraries \textbf{pandas}, \textbf{docx-mailmerge}, \textbf{nltk} Which Optimized Corresponding Workflow and Made Insurance Documents Production at Least 10 Times Faster.
    \item Developed Over 50 Other Micro-services for Facilitation of the Workflows Using \textbf{Python3} and \textbf{VBA} Which Facilitated Risk Data Collection \& Wrangling, Consolidation and Analysis.
\end{bullets}
\sectionsep

\resumeHeading{Chubb}{Multinational Underwriter}{Moscow, Russia}{Feb 2014 - Nov 2018}
\begin{bullets}
    \item Serviced the Portfolio of Large Multinational Clients, Circa 150 Insurance Policies per Year.
    \item Created and Delivered Various Scale Reports for Clients and Internal Stakeholders.
    \item Developed and Supported Spreadsheet Weekly Service Progress Reporting Tool Using \textbf{VBA} Which Made the Reports Production at Least 10 Times Faster.
    \item Developed a Number of Micro-services for Facilitation of the Workflows Using \textbf{VBA} and \textbf{Microsoft Mail Merge} Technology Which Facilitated Risk Data Collection \& Wrangling, Consolidation, Analysis and Insurance Documents Production.
    \item Designed \textbf{Microsoft Access} Database for Storing Risk Data Based on Multiple Input Sources Received as \textbf{.txt}, \textbf{.csv} and \textbf{ .xls(x)} Files.
\end{bullets}
\sectionsep

\resumeHeading{Mechel}{Marketing Analyst}{Moscow, Russia}{Jul 2013 - Oct 2013}
\begin{bullets}
    \item Developed Pricing Models for Sales Department;
    \item Contributed to Data Pipeline Project Using Data Collection from Various Data Sources, Like IHS McCloskey\'s, S\&P Global Platts etc., Data Consolidation, Interpretation and Analysis.
\end{bullets}
\sectionsep

\resumeHeading{Chubb}{Operations Specialist}{Moscow, Russia}{Apr 2012 - Jun 2013}
\begin{bullets}
    \item Implemented 10 Insurance Documentation Projects Using \textbf{Microsoft Mail Merge} Technology Based on \textbf{Microsoft Word} Template and \textbf{Microsoft Excel} Spreadsheet Which Made Documentation Production at Least 10 Times Faster \& Facilitated Control Over the Process.
    \item Operated Corporate Proprietary Database as the Client in Respect of Underwriting Information.
\end{bullets}
\sectionsep

\resumeHeading{State University of Management}{Staff Research Scientist}{Moscow, Russia}{Sep 2009 - Jun 2011}
\begin{bullets}
    \item Conducted Research in Economic \& Demographic Sciences; Produced the Official Research Report on Funded Work with the Team of Peer Researchers.
    \item Published 3 Research Papers. One of Those Papers Received Honors Degree Diploma at ``Eureka-2009'' Contest.
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{stat-can}{https://github.com/avtomatik/stat-can}{Python3, Regular Expressions, Data Science, Web Requests, Website Parsing}
A \href{https://www.statcan.gc.ca/}{Statistics Canada} Web Scraper for Sources Metadata. The program collects sources' metadata and distributes it to \textbf{Microsoft Excel} Spreadsheet.\\
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Main Concepts:}{Deep Learning, Design Patterns, Lazy Evaluation, Machine Learning, Mathematics, Object-Oriented Programming, Statistics}
    \\
    \singleItem{Languages:}{Python3, Bash, SQL, Visual Basic for Applications, HTML/CSS. Interested in Haskell \& Rust}
    \\
    \singleItem{Main Tools:}{Anaconda3, GitKraken, Jupyter Notebook, Linux, Visual Studio Code, pgAdmin4}
    \\
    \singleItem{Main Python Libraries/Frameworks:}{Django, Flask, NumPy, TensorFlow, pandas, sklearn, spaCy}
\end{skillList}


\section{Links}
\href{https://stackoverflow.com/users/10215873/alphamu}{Stack Overflow} $|$ \href{https://www.kaggle.com/alphamu}{Kaggle} $|$
\href{https://www.codewars.com/users/avtomatik}{Codewars} $|$
\href{https://www.hackerrank.com/kkruscherr}{Hackerrank} $|$
\href{https://leetcode.com/avtomatik/}{Leetcode}
\end{document}
